\documentclass[paper=a4,fontsize=15pt]{scrartcl}

% packages
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage{geometry}
\usepackage{mfirstuc}
\usepackage{anyfontsize}
\usepackage{soul}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{wrapfig}
\usepackage{sectsty}

\sectionfont{\fontsize{18}{10}\selectfont}

\titlespacing*{\section}
{0pt}{2.5ex plus 1ex minus .2ex}{1.2ex plus .2ex}

\pagestyle{empty}
\geometry{left=1.2cm, top=1.5cm, right=1.2cm, bottom=1.5cm, footskip=.5cm}

% set underscore \ul{} x pt below contents
\setul{2pt}{.4pt}

% set default font
\renewcommand{\familydefault}{\sfdefault}

% fat cdot
\makeatletter
\newcommand*\bigcdot{\mathpalette\bigcdot@{.5}}
\newcommand*\bigcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\makeatother

% macros ------------------------------------------------------------------------------
% -------------------------------------------------------------------------------------

% helpers
\newcommand{\smolboispace}{\vspace*{0.1em}}
\newcommand{\quarterspace}{\vspace*{0.25em}}
\newcommand{\halfspace}{\vspace*{0.5em}}
\newcommand{\bighalfspace}{\vspace*{0.75em}}
\newcommand{\fullspace}{\vspace*{1em}}

% header
\newcommand{\http}[1]{\href{http://#1}{\ul{#1}}}
\newcommand{\https}[1]{\href{https://#1}{\ul{#1}}}
\newcommand{\email}[1]{\href{mailto:#1}{\ul{#1}}}

% skills
\newcommand*{\newsummary}[2]{
  \noindent\hangafter=0\small
  {\capitalisewords{\textbf{#1}}: #2 \par}
}

% document ----------------------------------------------------------------------------
% -------------------------------------------------------------------------------------
\begin{document}

\begin{center}
  {\fontsize{35}{40}\selectfont Akshay Pall \par}
  \halfspace
  \smolboispace
  \smolboispace

  {\normalsize
    \email{akshay.pall@uwaterloo.ca}
    $\bigcdot$ \http{akshaypall.me}
    $\bigcdot$ \https{github.com/AkshayPall}
    \par}
\end{center}

\section*{Experience}{}
\normalsize
\noindent \href{https://bloomberg.com}{\textbf{\ul{Bloomberg}}}
$\vert$ \small Software Engineering Intern (Infrastructure)
{\hfill \footnotesize \textit{Jan 2020 - Present}}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \small
  \item Maintained and developed features for a
    \href{https://plot.ly/online-chart-maker/}{\ul{massive SaaS app}} built with
    React and Redux.
  \item Contributed to the development of an e2e testing framework written in
    Python Selenium.
\end{itemize}

\smolboispace
\smolboispace
\bighalfspace
\normalsize
\noindent \href{https://facebook.com}{\textbf{\ul{Facebook}}}
$\vert$ \small Software Engineering Intern (Distributed Database)
{\hfill \footnotesize \textit{May 2019 - Aug 2019}}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \small
  \item Added support for \textit{end-to-end exactly-once processing} semantics
    in \href{https://apache.github.io/incubator-heron/}{\ul{Apache Heron}} by
    implementing a variant of the two-phase commit algorithm. Details in
    \href{https://docs.google.com/document/d/1Shqp2z-uAhsOUN2erbc2d-72wdjA8anp}{\ul{design
        doc}}.
  \item Designed and implemented a system (in Scala) that made Twitter's
    interactive query infrastructure (Presto and Hive) GDPR-compliant.
\end{itemize}

\smolboispace
\smolboispace
\bighalfspace
\normalsize
\noindent \href{https://mail.yahoo.com}{\textbf{\ul{Oath}}}
$\vert$ \small Software Engineering Intern (Backend)
{\hfill \footnotesize \textit{Sep 2018 - Dec 2018}}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \small
  \item Implemented centralized authentication and path-based routing in
    PlanGrid's Kubernetes cluster using Envoy and Istio. This greatly improved
    developer productivity.
  \item Built Spinnaker pipelines to allow \textit{phased rollout} for
    ingress-related infrastructure changes.
  \item Contributed to the effort of instrumenting distributed tracing to
    improve visibility.
\end{itemize}

\smolboispace
\smolboispace
\bighalfspace
\normalsize
\noindent \href{https://mail.yahoo.com}{\textbf{\ul{Yahoo!}}}
$\vert$ \small Software Engineering Intern (Backend)
{\hfill \footnotesize \textit{Jan 2018 - Apr 2018}}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \small
  \item Worked on the metrics submission pipeline that streams millions of data
    points per second.
  \item Owned the time-series metadata creation service, written in Go, by
    ensuring its availability.
  \item Migrated the service's IPC layer to gRPC to improve reliability.
    Implemented consistent hashing and request termination, details in
    \href{http://lpan.io/migrating-to-grpc}{\ul{blog post}}.
\end{itemize}

\smolboispace
\smolboispace
\bighalfspace
\normalsize
\noindent \href{https://cbc.ca}{\ul{\textbf{CBC/Radio-Canada}}}
$\vert$ \small Native Apps Developer Coop (Android Product)
{\hfill \footnotesize \textit{May 2017 - Aug 2017}}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \small
  \item Developed many business-critical, A/B-tested, user-facing features
    using React and Rails.
  \item Pioneered and shipped Universe's first front-end app that consumes its
    new GraphQL API.
\end{itemize}

\section*{Writings}{}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \small
  \item \href{http://akshaypall.me}{\ul{TODO}} 
\end{itemize}

\section*{Education}{}
\noindent \textbf{University of Waterloo} Bachelor of Software Engineering \par
\quarterspace
\footnotesize
\noindent \textit{Sep 2016 - May 2021 (expected)} \par
\noindent 85\% cumulative GPA, \textit{2x Term Dean's Honours List}

\end{document}
